\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}

### 2009-11-09 AffineLieAlgebras/InformalNotes/article.tex
Something

Using the definition (\ref{fan-defined}) we get the following set of
the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$. 
Here we restricted the computation to the twelfth grade.
\begin{figure}[ph]
  \centering
  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:B4B2Fan}
\end{figure}

@@

Then after we have found all such weights $\nu$ and the corresponding branching coefficients $b^{(\mu)}_{\nu}$ we can substitute the sums $\sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}$ over the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules in place of the characters of the $\mathfrak{g}$-modules in the diagonal modular-invariant partition function
\begin{equation}
  \label{eq:34}
   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
\end{equation}
Thus we obtain the non-diagonal modular-invariant  partition function for the theory with the current algebra $\mathfrak{a}$.
\begin{equation}
  \label{eq:34}
   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
\end{equation}

>>>>

Using the definition (\ref{fan-defined}) we get the following set of
the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$: \ref{fig:AffineB2A1Fan}.
Here we restricted the computation to the twelfth grade.
\begin{figure}[ph]
  \centering
  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

@@

Then after we have found all such weights $\nu$ and the corresponding branching coefficients $b^{(\mu)}_{\nu}$ we can substitute the sums $\sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}$ over the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules in place of the characters of the $\mathfrak{g}$-modules in the diagonal modular-invariant partition function
\begin{equation}
  \label{eq:34}
   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
\end{equation}
Thus we obtain the non-diagonal modular-invariant  partition function for the theory with the current algebra $\mathfrak{a}$.
\begin{equation}
  \label{eq:36}
   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
\end{equation}
